\section{Introduction}

As of 2015, over 89 million people visit Yelp online per month \cite{yelp-stats}, whether it be to leave a review for a business or look up local restaurants to try. With so many users, there is naturally a massive amount of data being generated each day, so when Yelp Inc. released a dataset containing just about everything collected from their website over the past several years, many machine learning tasks immediately presented themselves. So then, given this vast dataset, what kinds of predictions/inferences can we make?

\subsection{Background}
Yelp is a website on which users can leave and read reviews about businesses, as well as find general information about those businesses, including hours of operation, menu, location, etc. Businesses on Yelp range from restaurants to salons to department stores, even to universities. Yelp also serves as a social media site, as reviewers can create profiles that display their location, favorite places, past reviews, and so on. Yelp's recently-released dataset includes all of this information and more. The main focus of this project is based on the fact that users can leave a star rating (a whole number between 1 and 5) for a business.

\subsection{Problem}
As with many domains in which one can leave reviews and ratings for something, a common task is to predict how positively or negatively that something will be rated by its audience (as in \cite{movie-ratings} for movies, \cite{youtube-ratings} for YouTube videos, and \cite{book-ratings} for books). Thus, Yelp lends itself to the machine learning task that we would like to address: can we predict the star rating a reviewer will give a business? Making accurate predictions about how a user will rate a business has applications in detecting spam (fake users leaving reviews that are inconsistent with their star ratings), more accurately aggregating user reviews to determine an overall star rating for a business, and recommending other businesses to Yelp users.